%!TEX TS-program = xelatex
\documentclass{nihbiosketch}

%------------------------------------------------------------------------------

\name{Matthis, Jonathan Samir}
\eracommons{jonmatthis} 
\position{Assistant Professor of Human Movement Neuroscience}

\begin{document}
%-----------------------------------------------------------------------------

\begin{education}
University of Maryland – Baltimore County  & BA           & 05/2007  & Philosophy \\
Rensselaer Polytechnic Institute               & MS         & 12/2011  & Cognitive Science \\
Rensselaer Polytechnic Institute               & PhD         & 09/2014  & Cognitive Science \\
University of Texas at Austi               & Postdoctoral         & 06/2019  & Pysch/Neuro Perceptual Systems \\
\end{education}


\section{Personal Statement}

\begin{statement}

        - big statement
        - human movement - science mentorship education
        - laser skeletons natural behavior 'the part of neuroscience tht overlaps with robotics' 
        - 2020 -> shift from emphasis on publications towards toolbuilding (free software as embodiment of scientific ideals)
        - building the next generation of scientific technology using free/open source software principles, while also training the next generation of thinkers doers healers and explorers


\begin{enumerate}

\item paper
       
\item Hunt, M.C., Jensen, J.L. \& Crenshaw, W. (2007). Substance abuse and
        mental health among community-dwelling elderly. International Journal
        of Geriatric Psychiatry, 24(9), 1124--1135.

\item Hunt, M.C., Wiechelt, S.A. \& Merryle, R. (2008). Predicting the
        substance-abuse treatment needs of an aging population.  American
        Journal of Public Health, 45(2), 236--245. PMCID: PMC9162292 
        
\item Hunt, M.C., Newlin, D.B. \& Fishbein, D. (2009). Brain imaging in
        methamphetamine abusers across the life-span. Gerontology, 46(3),
        122--145.

\end{enumerate}

\end{statement}

%------------------------------------------------------------------------------
\section{Positions, Scientific Appointments, and Honors}

\subsection*{Positions and Employment}
\begin{datetbl}
2007--      & Associate Professor, Department of Psychology, Washington University, St.\ Louis, MO\\
2002--2005  & Assistant Professor, Department of Psychology, Washington University, St.\ Louis, MO \\
2001--      & Consultant, Coastal Psychological Services, San Francisco, CA  \\
2000--2002  & Lecturer, Department of Psychology, Middlebury College, Middlebury, VT \\
1998--2000  & Fellow, Division of Intramural Research, National Institute of Drug Abuse, Bethesda, MD \\
\end{datetbl}

\subsection*{Other Experience and Professional Memberships}
\begin{datetbl}
2007--11         & NIH Risk, Adult Addictions Study Section, members \\
2003--           & Board of Advisors, Senior Services of Eastern Missouri \\
2003--05         & NIH Peer Review Committee: Psychobiology of Aging, ad hoc reviewer \\
2000--           & Associate Editor, Psychology and Aging \\ 
1998--           & Member, American Geriatrics Society \\
1998--           & Member, Gerontological Society of America \\
1995--           & Member, American Psychological Association \\
\end{datetbl}

\subsection*{Honors}
\begin{datetbl}
2009            & Award for Best in Interdisciplinary Ethnography, International Ethnographic Society \\
2004            & Excellence in Teaching, Washington University, St.\ Louis, MO \\
2003            & Outstanding Young Faculty Award, Washington University, St.\ Louis, MO \\
\end{datetbl}

%------------------------------------------------------------------------------

\section{Contribution to Science}

\begin{enumerate}
\item freemocap

\begin{enumerate}

\item Gryczynski, J., Shaft, B.M., Merryle, R., \& Hunt, M.C. (2002). Community
        based participatory research with late-life addicts. American Journal
        of Alcohol and Drug Abuse, 15(3), 222--238.

\item Shaft, B.M., Hunt, M.C., Merryle, R., \& Venturi, R. (2003). Policy
        implications of genetic transmission of alcohol and drug abuse in
        female nonusers. International Journal of Drug Policy, 30(5), 46--58.

\item Hunt, M.C., Marks, A.E., Shaft, B.M., Merryle, R., \& Jensen, J.L.
        (2004). Early-life family and community characteristics and late-life
        substance abuse. Journal of Applied Gerontology, 28(2),26--37.

\item Hunt, M.C., Marks, A.E., Venturi, R., Crenshaw, W. \& Ratonian, A.
        (2007). Community-based intervention strategies for reducing alcohol
        and drug abuse in the elderly.  Addiction, 104(9), 1436--1606. PMCID:
        PMC9000292

\end{enumerate}

\item laser skeletons

\begin{enumerate}

\item Gryczynski, J., Shaft, B.M., Merryle, R., \& Hunt, M.C. (2002). Community
        based participatory research with late-life addicts. American Journal
        of Alcohol and Drug Abuse, 15(3), 222--238.

\item Shaft, B.M., Hunt, M.C., Merryle, R., \& Venturi, R. (2003). Policy
        implications of genetic transmission of alcohol and drug abuse in
        female nonusers. International Journal of Drug Policy, 30(5), 46--58.

\item Hunt, M.C., Marks, A.E., Shaft, B.M., Merryle, R., \& Jensen, J.L.
        (2004). Early-life family and community characteristics and late-life
        substance abuse. Journal of Applied Gerontology, 28(2),26--37.

\item Hunt, M.C., Marks, A.E., Venturi, R., Crenshaw, W. \& Ratonian, A.
        (2007). Community-based intervention strategies for reducing alcohol
        and drug abuse in the elderly.  Addiction, 104(9), 1436--1606. PMCID:
        PMC9000292

\end{enumerate}


\item retinal flow  

\begin{enumerate}

\item Hunt, M.C., Merryle, R. \& Jensen, J.L. (2005). The effect of social
        support networks on morbidity among elderly substance abusers. Journal
        of the American Geriatrics Society, 57(4), 15--23.

\item Hunt, M.C., Pour, B., Marks, A.E., Merryle, R. \& Jensen, J.L. (2005).
        Aging out of methadone treatment. American Journal of Alcohol and Drug
        Abuse, 15(6), 134--149. 

\item Merryle, R. \& Hunt, M.C. (2007). Randomized clinical trial of cotinine
        in older nicotine addicts. Age and Ageing, 38(2), 9--23. PMCID:
        PMC9002364

\end{enumerate}

\item visual control of foot placement (fajen era)

\begin{enumerate}   

\item Hunt, M.C. \& Jensen, J.L. (2003). Morbidity among elderly substance
        abusers. Journal of the Geriatrics, 60(4), 45--61.

\item Hunt, M.C. \& Pour, B. (2004). Methadone treatment and personal
        assessment. Journal Drug Abuse, 45(5), 15--26. 

\item  Merryle, R. \& Hunt, M.C. (2005). The use of various nicotine delivery
        systems by older nicotine addicts. Journal of Ageing, 54(1), 24--41.
        PMCID: PMC9112304

\item Hunt, M.C., Jensen, J.L. \& Merryle, R. (2008). The aging addict:
        ethnographic profiles of the elderly drug user.  NY, NY: W. W. Norton
        \& Company.

\end{enumerate}

\end{enumerate}

\subsection*{Complete List of Published Work in MyBibliography:} 
\url{http://www.ncbi.nlm.nih.gov/myncbi/browse/collection/45972964/}



\end{document}


%------------------------------------------------------------------------------

\section{Research Support}

\subsection*{Ongoing Research Support}

\grantinfo{R01 DA942367}{Hunt (PI)}{09/01/08--08/31/16}
{Health trajectories and behavioral interventions among older substance abusers}
{The goal of this study is to compare the effects of two substance abuse interventions on health 
outcomes in an urban population of older opiate addicts.}
{Role: PI}

\bigskip

\grantinfo{R01 MH922731}{Merryle (PI)}{12/15/07--11/30/15}
{Physical disability, depression and substance abuse in the elderly}
{The goal of this study is to identify disability and depression trajectories and demographic factors 
associated with substance abuse in an independently-living elderly population.}
{Role: Co-Investigator}

\bigskip

\grantinfo{Faculty Resources Grant, Washington University}{08/15/09--08/14/15}
{Opiate Addiction Database}
{The goal of this project is to create an integrated database of demographic, social and biomedical 
information for homeless opiate abusers in two urban Missouri locations, using a number of state and 
local data sources.}
{Role: PI}


%------------------------------------------------------------------------------

\subsection*{Completed Research Support}

\grantinfo{R21 AA998075}{Hunt (PI)}{01/01/11--12/31/13}
{Community-based intervention for alcohol abuse}
{The goal of this project was to assess a community-based strategy for reducing alcohol abuse among 
older individuals.}
{Role: PI}
